### 2021-04-22 input/related_work.tex
update label
some spacing and figure placement
rework related work

\section{Related Work}
\label{related_work}

In the context of this paper, a content indexing service enables that for any content, every node is able to access its closest replica.
Basically, offering such a service requires (i) to have access to the list of current replica localizations, (ii) to be aware of the topology to compute which replica is the closest for a given location.

(i) Deploying a centralized server that maintain an index of all replica localizations has been proposed~\cite{fogstore, p2p-alto, p2p-oracle, snamp}. However, this solution suffers from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in an Edge context.
Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example. In the latter, each node stores a part of the index, defined by an interval between hash values. 
Before downloading any object, a node first
hashes the content to obtain the address of the node that stores the replica localizations of this given object. After obtaining from the remote node the list of available replicas, it can select the closest copy to download from. We emphasize that, in this setting, the DHT only stores information about replicas localizations, not the content itself. DHT-based approaches are well-studied and easy to deploy in order to offer such a localization service.

(ii) Being centralized or distributed, this index should be enhanced with the topology knowledge in order to be able to decide where resides the closest replica . Maintaining a consistent view of an ever changing topology accross a network is ihnerently complicated, especially in asynchronous settings. This is a well-studied problem in the network community and numerous protocols have been proposed. As for the index, this knowledge about the topology can be either centralized[REF] or distributed[REF].

However, solutions that require to contact a remote node (either a server or a DHT node) to request this index usually implies reaching nodes out of the their geographical scope, as already explained.
At first glance, membership protocols as proposed in~\cite{t-man} would appear to provide suitable abstractions to create a scope-related partioning, as proposed in this paper. Yet, such protocols usually rely on gossip mechanims, implying contacts with random nodes that can be very far away in the physical topology. Moreover, membership protocols are designed to generate logical overlays by modifying the neighboring of a given node according to a given metric. 
On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node are not continusously modifed. Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change.
Finally, we emphasize that consistency is at the core of our design, as \NAME provides the same guarantees for all nodes.
On the contrary, to avoid flooding, authors in~\cite{opnl} propose to propagate information about cache updates only towards the original replica. This enables for a request to be caught \textit{on-path}, and be redirected to the closest replica. However, the announcement is only performed towards this original replica, that is requests can miss closer replicas that are not on this path, thus decreasing the efficiency of the cache sharing mechanism.

>>>>

\section{Related Work}
\label{sec:related_work}
Content indexing in geo-distributed infrastructures has been studied through various approaches. 
Offering an indexing service which is either hosted by a centralized entity or distributed through nodes of the network has long been the predominant one. This mainly requires (i) to have access to the list of current replica locations and (ii) to be aware of the topology to compute which replica is the closest for a given location.

(i) Deploying a centralized server that maintains an index of all replica locations has been proposed in~\cite{fogstore, p2p-alto, p2p-oracle, snamp}. These solutions suffer from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in an Edge context.
Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, mdht} for example. In the latter, each node stores a part of the index, defined by an interval between hash values. 
Before downloading any object, a node first
hashes the content to obtain the address of the node that stores the replica locations of this given object. After obtaining from the remote node the list of available replicas, it can select the closest copy to download from. We emphasize that, in this setting, the DHT only stores information about replicas locations, not the content itself. DHT-based approaches are well-studied and easy to deploy in order to offer such a localization service.

(ii) Being centralized or distributed, this index should be enhanced with the topology knowledge in order to be able to decide where resides the closest replica . Maintaining a consistent view of an ever changing topology accross a network is ihnerently complicated, especially in asynchronous settings. This is a well-studied problem in the network community and numerous protocols have been proposed. As for the index, this knowledge about the topology can be either centralized~\cite{topology-discovery} or distributed like in routing protocols such as OSPF (Open Shortest Path First).
All these solutions require to contact a remote node (either a server or a DHT node) to request this index 
which is costly in terms of latency while in contradiction with Edge infrastructure constraints, as previsouly explained.

The opposite approach consists in hosting the index directly on the nodes, avoiding any prior request to access a content.   
%This requires notifying nodes of replica creations and removals along with information about the evolving topology. 
Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica locations for all nodes~\cite{nlsr}. Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node.
Similarly, one could solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. Yet both solutions inherently imply that every nodes will eventually receive all messages.

At first glance, membership protocols as proposed in~\cite{t-man} would appear to provide suitable abstractions to create a scope-related partioning, as proposed in this paper. Such protocols usually rely on gossip mechanims, implying contacts with random nodes that can be very far away in the physical topology. Moreover, membership protocols are designed to generate logical overlays by modifying the neighboring of a given node according to a given metric. 
On the contrary, we do not aim at building any overlay, as we only rely on the physical topology so the neighbors of a given node are not continusously modifed. Lastly, these protocols are usually cycle-based, meaning that they impose a constant load on the network traffic, even when the system state does not change. Likewise, this also prevents from using solutions that periodically advertise their cache content~\cite{hemmati2015namebased, garcia-lopez} as they also inccur an overhead even in quiet contexts without any update. 
Moreoever, such solutions necessarily rely on physical timeouts that could lead to either premature removals of partitions when they are still operating; or slow convergence where processes wrongly believe they belong to a partition that was removed.

%Finally, we emphasize that consistency is at the core of our design, as \NAME provides the same guarantees for all nodes.
%On the contrary, to avoid flooding, authors in~\cite{opnl} propose to propagate information about cache updates only towards the original replica. This enables for a request to be caught \textit{on-path}, and be redirected to the closest replica. However, the announcement is only performed towards this original replica, that is requests can miss closer replicas that are not on this path, thus decreasing the efficiency of the cache sharing mechanism.
